### 2023-12-08 paper/content.tex
Update the Open Research section

The Python source code used to produce all results and figures presented here, as well as supplemental figures and Jupyter notebooks, are available from \citet{sourcearchive}, also available on \url{https://github.com/\GitHubRepository} under the MIT and CC-BY licenses.
The QDM magnetic microscopy data are available
from \citet{janinedata} under the CC-0 license.

>>>>

The Python source code used to produce all results and figures presented here, as well as supplemental figures and Jupyter notebooks, are available from \citet{sourcearchive}, which can also be found on \url{https://github.com/\GitHubRepository} under the MIT and CC-BY licenses.
The QDM magnetic microscopy data are available
from \citet{janinedata} under the CC-0 license.
